### 2024-02-28 ms.qmd
Updates

 We found that the learning slopes for all treatments and species were higher from zero (@tbl-data), but we did not find any difference between treatments or species in the learning rate (@fig-results). There were not significant differences between treatments in _L. delicata_ (Control-Cold - CORT-Cold = `r format_dec(mean(deli_ControlCold - deli_CORTCold), 3)`, p- value = `r format_dec(pmcmc(deli_ControlCold - deli_CORTCold), 3)`; Control-Hot - CORT-Hot = `r format_dec(mean(deli_ControlHot - deli_CORTHot), 3)`, p- value = `r format_dec(pmcmc(deli_ControlHot - deli_CORTHot), 3)`; Control-Hot - Control-Cold = `r format_dec(mean(deli_ControlHot - deli_ControlCold), 3)`, p-value = `r format_p(pmcmc(deli_ControlHot - deli_ControlCold), 3)`; CORT-Hot - CORT-Cold = `r format_dec(mean(deli_CORTHot - deli_CORTCold), 3)`, p-value = `r format_p(pmcmc(deli_CORTHot - deli_CORTCold), 3)`) (see @fig-results) or _L. guichenoti_ (Control-Cold - CORT-Cold = `r format_dec(mean(guich_ControlCold - guich_CORTCold), 3)`, p- value = `r format_dec(pmcmc(guich_ControlCold - guich_CORTCold), 3)`; Control-Hot - CORT-Hot = `r format_dec(mean(guich_ControlHot - guich_CORTHot), 3)`, p- value = `r format_dec(pmcmc(guich_ControlHot - guich_CORTHot), 3)`; Control-Hot - Control-Cold = `r format_dec(mean(guich_ControlHot - guich_ControlCold), 3)`, p-value = `r format_p(pmcmc(guich_ControlHot - guich_ControlCold), 3)`; CORT-Hot - CORT-Cold = `r format_dec(mean(guich_CORTHot - guich_CORTCold), 3)`, p-value = `r format_p(pmcmc(guich_CORTHot - guich_CORTCold), 3)`) (see @fig-results).  
 We compared each factor (hormone and incubation temperature) separately by pooling together the observations for all the individuals from the same hormone treatment or the same incubation temperature. In this regard, we did not find any significant effect of the hormone treatment (_L. delicata_: Control learning slope - CORT learning slope = `r format_dec(mean((deli_ControlCold + deli_ControlHot) - (deli_CORTCold + deli_CORTHot)), 3)`, p-value = `r format_p(pmcmc((deli_ControlCold + deli_ControlHot) - (deli_CORTCold + deli_CORTHot)), 3)`; _L. guichenoti_: Control learning slope - CORT learning slope = `r format_dec(mean((guich_ControlCold + guich_ControlHot)-(guich_CORTCold + guich_CORTHot)), 3)`, p-value = `r format_p(pmcmc((guich_ControlCold + guich_ControlHot)-(guich_CORTCold + guich_CORTHot)), 3)`) or the incubation temperature (_L. delicata_: Hot learning slope - Cold learning slope = `r format_dec(mean((deli_CORTHot + deli_ControlHot) - (deli_CORTCold + deli_ControlCold)),3)`, p-value = `r format_p(pmcmc((deli_CORTHot + deli_ControlHot) - (deli_CORTCold + deli_ControlCold)),3)`; _L. guichenoti_: Hot learning slope - Cold learning slope = `r format_dec(mean((guich_CORTHot + guich_ControlHot) - (guich_CORTCold + guich_ControlCold)),3)`, p-value = `r format_p(pmcmc((guich_CORTHot + guich_ControlHot) -(guich_CORTCold + guich_ControlCold)),3)`) in either species.  
 Finally, when all individuals from all the treatments were pooled together and species were compared, there were not significant differences in the estimated slopes (_L. delicata_ - _L. guichenoti_ = `r format_dec(mean((deli_CORTCold + deli_ControlCold + deli_CORTHot + deli_ControlHot) - (guich_CORTCold + guich_ControlCold + guich_CORTHot + guich_ControlHot)), 3)`, p-value = `r format_p(pmcmc((deli_CORTCold + deli_ControlCold + deli_CORTHot + deli_ControlHot) - (guich_CORTCold + guich_ControlCold + guich_CORTHot + guich_ControlHot)), 3)`).

>>>>

 We found that the learning slopes for all treatments and species were higher from zero (@tbl-data), but we did not find any difference between treatments or species in the learning rate (@fig-results). For _L. delicata_, we did not find any significant effects of the hormone (Control - CORT = `r format_dec(mean((deli_ControlCold + deli_ControlHot) - (deli_CORTCold + deli_CORTHot)), 3)`, p-value = `r format_p(pmcmc((deli_ControlCold + deli_ControlHot) - (deli_CORTCold + deli_CORTHot)), 3)`), incubation temperature (Hot - Cold = `r format_dec(mean((deli_CORTHot + deli_ControlHot) - (deli_CORTCold + deli_ControlCold)),3)`, p-value = `r format_p(pmcmc((deli_CORTHot + deli_ControlHot) - (deli_CORTCold + deli_ControlCold)),3)`), or the interaction ([(Control-Hot - CORT-Hot) - (Control-Cold - CORT-Cold)] = `r format_dec(mean((deli_ControlHot - deli_CORTHot)-(deli_ControlCold - deli_CORTCold)), 3)`).  
 For _L. guichenoti_, we did not find any significant effects of the hormone (Control - CORT = `r format_dec(mean((guich_ControlCold + guich_ControlHot) - (guich_CORTCold + guich_CORTHot)), 3)`, p-value = `r format_p(pmcmc((guich_ControlCold + guich_ControlHot) - (guich_CORTCold + guich_CORTHot)), 3)`), incubation temperature (Hot - Cold = `r format_dec(mean((guich_CORTHot + guich_ControlHot) - (guich_CORTCold + guich_ControlCold)),3)`, p-value = `r format_p(pmcmc((guich_CORTHot + guich_ControlHot) - (guich_CORTCold + guich_ControlCold)),3)`), or the interaction ([(Control-Hot - CORT-Hot) - (Control-Cold - CORT-Cold)] = `r format_dec(mean((guich_ControlHot - guich_CORTHot) - (guich_ControlCold - guich_CORTCold)), 3)`).  
Finally, when all individuals from all the treatments were pooled together and species were compared, there were not significant differences in the estimated slopes (_L. delicata_ - _L. guichenoti_ = `r format_dec(mean((deli_CORTCold + deli_ControlCold + deli_CORTHot + deli_ControlHot) - (guich_CORTCold + guich_ControlCold + guich_CORTHot + guich_ControlHot)), 3)`, p-value = `r format_p(pmcmc((deli_CORTCold + deli_ControlCold + deli_CORTHot + deli_ControlHot) - (guich_CORTCold + guich_ControlCold + guich_CORTHot + guich_ControlHot)), 3)`).

There were not significant differences between treatments in _L. delicata_ (Control-Cold - CORT-Cold = `r format_dec(mean(deli_ControlCold - deli_CORTCold), 3)`, p- value = `r format_dec(pmcmc(deli_ControlCold - deli_CORTCold), 3)`; Control-Hot - CORT-Hot = `r format_dec(mean(deli_ControlHot - deli_CORTHot), 3)`, p- value = `r format_dec(pmcmc(deli_ControlHot - deli_CORTHot), 3)`; Control-Hot - Control-Cold = `r format_dec(mean(deli_ControlHot - deli_ControlCold), 3)`, p-value = `r format_p(pmcmc(deli_ControlHot - deli_ControlCold), 3)`; CORT-Hot - CORT-Cold = `r format_dec(mean(deli_CORTHot - deli_CORTCold), 3)`, p-value = `r format_p(pmcmc(deli_CORTHot - deli_CORTCold), 3)`) (see @fig-results) or _L. guichenoti_ (Control-Cold - CORT-Cold = `r format_dec(mean(guich_ControlCold - guich_CORTCold), 3)`, p- value = `r format_dec(pmcmc(guich_ControlCold - guich_CORTCold), 3)`; Control-Hot - CORT-Hot = `r format_dec(mean(guich_ControlHot - guich_CORTHot), 3)`, p- value = `r format_dec(pmcmc(guich_ControlHot - guich_CORTHot), 3)`; Control-Hot - Control-Cold = `r format_dec(mean(guich_ControlHot - guich_ControlCold), 3)`, p-value = `r format_p(pmcmc(guich_ControlHot - guich_ControlCold), 3)`; CORT-Hot - CORT-Cold = `r format_dec(mean(guich_CORTHot - guich_CORTCold), 3)`, p-value = `r format_p(pmcmc(guich_CORTHot - guich_CORTCold), 3)`) (see @fig-results).
We compared each factor (hormone and incubation temperature) separately by pooling together the observations for all the individuals from the same hormone treatment or the same incubation temperature. In this regard, we did not find any significant effect of the hormone treatment (_L. delicata_: Control learning slope - CORT learning slope = `r format_dec(mean((deli_ControlCold + deli_ControlHot) - (deli_CORTCold + deli_CORTHot)), 3)`, p-value = `r format_p(pmcmc((deli_ControlCold + deli_ControlHot) - (deli_CORTCold + deli_CORTHot)), 3)`; _L. guichenoti_: Control learning slope - CORT learning slope = `r format_dec(mean((guich_ControlCold + guich_ControlHot)-(guich_CORTCold + guich_CORTHot)), 3)`, p-value = `r format_p(pmcmc((guich_ControlCold + guich_ControlHot)-(guich_CORTCold + guich_CORTHot)), 3)`) or the incubation temperature (_L. delicata_: Hot learning slope - Cold learning slope = `r format_dec(mean((deli_CORTHot + deli_ControlHot) - (deli_CORTCold + deli_ControlCold)),3)`, p-value = `r format_p(pmcmc((deli_CORTHot + deli_ControlHot) - (deli_CORTCold + deli_ControlCold)),3)`; _L. guichenoti_: Hot learning slope - Cold learning slope = `r format_dec(mean((guich_CORTHot + guich_ControlHot) - (guich_CORTCold + guich_ControlCold)),3)`, p-value = `r format_p(pmcmc((guich_CORTHot + guich_ControlHot) -(guich_CORTCold + guich_ControlCold)),3)`) in either species.
Finally, when all individuals from all the treatments were pooled together and species were compared, there were not significant differences in the estimated slopes (_L. delicata_ - _L. guichenoti_ = `r format_dec(mean((deli_CORTCold + deli_ControlCold + deli_CORTHot + deli_ControlHot) - (guich_CORTCold + guich_ControlCold + guich_CORTHot + guich_ControlHot)), 3)`, p-value = `r format_p(pmcmc((deli_CORTCold + deli_ControlCold + deli_CORTHot + deli_ControlHot) - (guich_CORTCold + guich_ControlCold + guich_CORTHot + guich_ControlHot)), 3)`).
